\documentclass[10pt]{article}
%\usepackage{anysize}
%\papersize{11in}{8.5in}
%\marginsize{1in}{1in}{.5in}{.5in}
\textwidth = 6.5 in
\textheight = 9 in
\oddsidemargin = 0.0 in
\evensidemargin = 0.0 in
\topmargin = -0.5 in
\headheight = 0.35 in
\headsep = 0.15 in
\topskip = 0 in
\footskip = 0.5 in
\pagenumbering{arabic}
\usepackage{setspace}
\usepackage[usenames]{color}
\usepackage[fleqn]{amsmath}
\usepackage{graphicx}
\usepackage{url}
\usepackage{verbatim}
\usepackage{indentfirst}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{ragged2e}
\usepackage{xspace}
\usepackage{parskip}
\usepackage{tabulary}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\hypersetup{pdfborder={0 0 0}, colorlinks=true, urlcolor=blue, linkcolor=black}
\usepackage{titlesec}
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{ifthen}

\usepackage[round]{natbib}
\bibliographystyle{evolution}

%% Format headers and footers %%%%%%%%%%%%%%%%%%%%
\pagestyle{fancy}
%\lhead{\ifthenelse{\value{page}=1}{}{\sffamily\footnotesize Jamie Oaks}}
\lhead{\sffamily \emph{\docTitle} \\ Jamie R. Oaks}
%\chead{\ifthenelse{\value{page}=1}{{\scshape \docTitle} \\ Jamie Richard Oaks}{\sffamily\footnotesize \docTitle}}
%\rhead{\ifthenelse{\value{page}=1}{}{\sffamily\footnotesize \today}}
\rhead{\sffamily \today}
\cfoot{\sffamily\footnotesize Page \thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}

%% Format section titles %%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand\refname{Peer-reviewed Publications}

\titleformat{\section}[hang]
    {\large\sffamily\bfseries}
    {\S\ \thesection.}{.5em}{}[]
\titlespacing{\section}
    {0mm}{1.0ex plus .1ex minus .1ex}{-0.5ex}

\titleformat{\subsection}[hang]
    {\large\sffamily\itshape}
    {\S\ \thesection.}{.5em}{}[]
\titlespacing{\subsection}
    {0mm}{1.0ex plus .1ex minus .1ex}{-0.5ex}

\titleformat{\subsubsection}[runin]
    {\sffamily\itshape}
    {\S\ \thesection.}{.5em}{}[.---]
\titlespacing{\subsubsection}
    {\parindent}{0pt}{0pt}
%    {\parindent}{1.0ex plus .1ex minus .1ex}{0pt}

%% Format list environments %%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}}
\renewcommand{\labelitemi}{$\circ$}

\newenvironment{myEnumerate}{
  \begin{enumerate}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.5em}}
  {\end{enumerate}}

\newenvironment{myItemize}{
  \begin{itemize}
    \setlength{\leftskip}{-4mm}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.5em}}
  {\end{itemize}}

%% Basic formatting and spacing %%%%%%%%%%%%%%%%%%%%%
\setlength{\parindent}{0em}
\setlength{\parskip}{0.5em}

%% My functions %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\ignore}[1]{}
\newcommand{\addTail}[1]{\textit{#1}.---}
\newcommand{\super}[1]{\ensuremath{^{\textrm{#1}}}}
\newcommand{\sub}[1]{\ensuremath{_{\textrm{#1}}}}
\newcommand{\dC}{\ensuremath{^\circ{\textrm{C}}}}
\newcommand{\tableSubItem}{\addtolength{\leftskip}{1em} \labelitemi \xspace}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\docTitle}{Teaching Effectiveness\xspace}
\begin{document}
% \raggedright
\singlespacing

%\section*{Teaching Appointments \& Evaluation Comments}
As a graduate student, I have had the privilege of being a teaching assistant for
introductory courses in Biostatistics and Genetics.
For the latter, I was awarded the Kenneth B.\ Armitage Award for Excellence in
Teaching; an award given by the University of Kansas Division of Biological
Sciences to an outstanding graduate teaching assistant that is nominated by
their students.
Below are a selection of comments from my students from each class.

\begin{multicols}{2}
% \subsection*{Biology 350---Genetics---Fall 2010}
\subsection*{Biology 350---Genetics}
\begin{myItemize}
\sffamily
\item ``Thank you so so much for reviews\ldots If you want to be in academics later, you'll be an excellent professor.''
\item ``He was an awesome TA! Loved his review sessions---very helpful''
\item ``The instructor presented information \underline{very} well, answered questions clearly and took the time to give thorough reviews for exams.''
\item ``The instructor always took time to answer questions about homework and went out of his way to help students study for exams in the class.''
\item ``Jamie was open to questions \& explained things in a way that was easy to understand.''
\item ``Made hard concepts easy to understand.''
\item ``Very helpful; often scheduled review sessions on his own time.''
\item ``Very approachable---had lots of knowledge of material \& explained topics very well.''
\item ``Jamie was enthusiastic \& helpful.''
\item ``Really great teacher. Explained things well. Better than the professors.''
\item ``Instructor explained well, made sure class understood material. Enjoyed the instructor, class was great!''
\item ``His teaching is good. He is easy to understand.''
\item ``He was very helpful and made himself very available for questions/reviews.''
% \end{myItemize}

% \subsection*{Biology 350---Genetics---Spring 2010}
% \begin{myItemize}
% \sffamily
\item ``Jamie is the best TA!''
\item ``Jamie is one of the best TAs I've had. Very
helpful \& explains things very well. He never just assumed or
expected that we knew things\ldots he took the time to explain it.''
\item ``Jamie is one of the best TAs I've ever had. He explains the subject
very well, answers questions and always ready to help.''
\item ``Very clear in his teaching. Very knowledgeable about the material.''
\item ``Would try several ways to explain topics that were not easily
understood.''
\item ``Always helpful, appreciated that he went over homework, and explained things thoroughly.''
\item ``He explained concepts in simple terms \& was able to clarify questions from lecture.''
\item ``Very real \& down to earth. Available \& explains concepts well.''
\item ``I like how Jamie is organized in discussion and also that he explains the material very well.''
\item ``Course is well organized, interactive. Best instructor ever!''
\item ``I really enjoyed the class, and I appreciated the help during office hours. Also, very understanding about class conflicts.''
\item ``He did a good job teaching a class during a difficult time---late in the day when students don't have a long attention span.''
\item ``Jamie is very helpful \& always responds to students needs promptly.''
\item ``Very calm, nice \& very helpful.''
\item ``Jamie is a great TA. Easy to understand, knows his stuff, willing to
take time and explain topics.''
\item ``He was responsive to emails \& explained things well.''
\end{myItemize}
% \end{multicols}

% \subsection*{Biology 570---Biostatistics---Fall 2009}
% \begin{multicols}{2}
\subsection*{Biology 570---Biostatistics}
\begin{myItemize}
\sffamily
\item ``Jamie was really nice and patient with everyone.''
\item ``Attentive, helpful.''
\item ``Taught very well.''
\item ``Easy to talk to, approachable.''
\item ``Very helpful in lab.''
\item ``He was very helpful, helped me learn the material, and seemed to care
about everyone learning and doing well.''
\item ``Instructor knew the material well.''
\item ``Willing to meet outside class.''
\item ``Jamie was really patient and explained things very clearly.''
\item ``Helpful and knowledgeable TA.''
\item ``Always willing to go out of his way to help people and make sure
everyone is on the same page.''
\item ``Jamie was an excellent TA. Did a great job of explaining.''
\item ``Lots of office hours making it easy to get help.''
\item ``He was very helpful and clear.''
\end{myItemize}
\end{multicols}


\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
