%\section*{Teaching Appointments \& Evaluation Comments}
As a graduate student, I had the privilege of being a teaching assistant for
introductory courses in Biostatistics and Genetics.
For the latter, I was awarded the Kenneth B.\ Armitage Award for Excellence in
Teaching; an award given by the University of Kansas Division of Biological
Sciences to an outstanding graduate teaching assistant that is nominated by
their students.
Below are comments by my students from my teaching evaluations for these
classes.

\begin{multicols}{2}
% \subsection*{Biology 350---Genetics---Fall 2010}
\subsection*{Biology 350---Genetics}
\begin{myItemize}
\sffamily
\item ``Thank you so so much for reviews\ldots If you want to be in academics later, you'll be an excellent professor.''
\item ``He was an awesome TA! Loved his review sessions---very helpful''
\item ``The instructor presented information \underline{very} well, answered questions clearly and took the time to give thorough reviews for exams.''
\item ``The instructor always took time to answer questions about homework and went out of his way to help students study for exams in the class.''
\item ``Jamie was open to questions \& explained things in a way that was easy to understand.''
\item ``Made hard concepts easy to understand.''
\item ``Very helpful; often scheduled review sessions on his own time.''
\item ``Very approachable---had lots of knowledge of material \& explained topics very well.''
\item ``Jamie was enthusiastic \& helpful.''
\item ``Really great teacher. Explained things well. Better than the professors.''
\item ``Instructor explained well, made sure class understood material. Enjoyed the instructor, class was great!''
\item ``His teaching is good. He is easy to understand.''
\item ``He was very helpful and made himself very available for questions/reviews.''
% \end{myItemize}

% \subsection*{Biology 350---Genetics---Spring 2010}
% \begin{myItemize}
% \sffamily
\item ``Jamie is the best TA!''
\item ``Jamie is one of the best TAs I've had. Very
helpful \& explains things very well. He never just assumed or
expected that we knew things\ldots he took the time to explain it.''
\item ``Jamie is one of the best TAs I've ever had. He explains the subject
very well, answers questions and always ready to help.''
\item ``Very clear in his teaching. Very knowledgeable about the material.''
\item ``Would try several ways to explain topics that were not easily
understood.''
\item ``Always helpful, appreciated that he went over homework, and explained things thoroughly.''
\item ``He explained concepts in simple terms \& was able to clarify questions from lecture.''
\item ``Very real \& down to earth. Available \& explains concepts well.''
\item ``I like how Jamie is organized in discussion and also that he explains the material very well.''
\item ``Course is well organized, interactive. Best instructor ever!''
\item ``I really enjoyed the class, and I appreciated the help during office hours. Also, very understanding about class conflicts.''
\item ``He did a good job teaching a class during a difficult time---late in the day when students don't have a long attention span.''
\item ``Jamie is very helpful \& always responds to students needs promptly.''
\item ``Very calm, nice \& very helpful.''
\item ``Jamie is a great TA. Easy to understand, knows his stuff, willing to
take time and explain topics.''
\item ``He was responsive to emails \& explained things well.''
\end{myItemize}
% \end{multicols}

% \subsection*{Biology 570---Biostatistics---Fall 2009}
% \begin{multicols}{2}
\subsection*{Biology 570---Biostatistics}
\begin{myItemize}
\sffamily
\item ``Jamie was really nice and patient with everyone.''
\item ``Attentive, helpful.''
\item ``Taught very well.''
\item ``Easy to talk to, approachable.''
\item ``Very helpful in lab.''
\item ``He was very helpful, helped me learn the material, and seemed to care
about everyone learning and doing well.''
\item ``Instructor knew the material well.''
\item ``Willing to meet outside class.''
\item ``Jamie was really patient and explained things very clearly.''
\item ``Helpful and knowledgeable TA.''
\item ``Always willing to go out of his way to help people and make sure
everyone is on the same page.''
\item ``Jamie was an excellent TA. Did a great job of explaining.''
\item ``Lots of office hours making it easy to get help.''
\item ``He was very helpful and clear.''
\end{myItemize}
\end{multicols}

